Clustering Beat-Chroma Patterns\\ in a Large Music Database

### 2010-03-24 Paper/Paper.tex
tiny improvements

\subsection{Cluster}
Once we understand the kind of codebook we create, we naturally want
to visualize the clusters, \ie the patterns from actual song that
surround a given centroid. Unsurprisingly, real patterns tend to be
noisier than codes. However, centroids seem to capture important aspects
of the patterns. We could compare the centroids with the result of
a lowpass filtering. In Figure \ref{fig:cluster} we show elements of the same
cluster, and in Figure \ref{fig:cluster_diff}, we emphasize the difference
with the centroid. We hope for the difference to look uniformly random,
the result seems to fit that assumption.

@@

Moving on to larger scales, we could imagine merging codes together and
splitting some on two if the clusters become too small or too large.We could
also cluster the codebook itself, in a similar fashion as hierarchical
Gaussian mixtures \cite{Vasconcelos2001}.
%  (similar idea used for indexing \cite{Muja2009})

>>>>

\subsection{Cluster}
Visualizing a codebook is half of the story, we also want to understand
clusters, \ie the patterns from actual song that
surround a given centroid (codeword). Unsurprisingly, real patterns are
noisier than codes. However, centroids seem to capture important aspects
of the patterns. We could compare the centroids with the result of
a lowpass filtering. In Figure \ref{fig:cluster} we show elements of the same
cluster, and in Figure \ref{fig:cluster_diff}, we emphasize the difference
with the centroid. We hope for the difference to look uniformly random,
the result seems to fit that assumption.

@@

Moving on to larger scales, we could imagine merging codes together and
splitting some on two if the clusters become too small or too large.We could
also cluster codebooks themselves, in a similar fashion as hierarchical
Gaussian mixtures \cite{Vasconcelos2001}.
%  (similar idea used for indexing \cite{Muja2009})
